Plots_OceanProtein

### 2024-05-31 Code/Plots_OceanProtein.Rmd
no change, was going to change the ggsave size but decided on default

 ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroPhotosynthDepthO2.png")), device = NULL, scale = 1, height=15, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
 ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "PLOSRound2", "Fig2.tiff")), device = NULL, scale = 1, height=15, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)

@@

   ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroProteinMetabDepthO2.png")), device = NULL, scale = 1, height=15, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
   ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "PLOSRound2", "Fig10.tiff")), device = NULL, scale = 1, height=15, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)

>>>>

 ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroPhotosynthDepthO2.png")))
 ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "PLOSRound2", "Fig2.tiff")))

@@

   ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroProteinMetabDepthO2.png")))
   ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "PLOSRound2", "Fig10.tiff")))
